Concurrent Programming with Harmony

### 2020-08-11 book/paper.tex
Added some more details on the virtual machine

Details:
\begin{itemize}
\item The name in a name tag is the name of the method that the process
is executing;
\item The tag in a name tag the argument to the method by default.  Optionally
\texttt{spawn} allows the tag to be specified explicitly;
\item The frame pointer points to the current \emph{stack frame},
which consists of the caller's frame and variables, the argument to
the method, and the return address.
\item A process terminates when it reaches the \texttt{Return} instruction
of the method or when it hits an exception.  Exceptions include divide by zero,
reading a non-existent key in a dictionary, accessing a non-existent
variable, as well as when an assertion fails;
\item The execution of a process in \emph{atomic mode} does not get interleaved
with that of other processes.
\item The register of a process always contains a dictionary, mapping
atoms to arbitrary values.  The atoms correspond to the variable names
in a Harmony program.
\end{itemize}

@@

@@

Because tuples and lists are dictionaries, the \texttt{del} statement is
different Python.  For example, if $x$ = [.a, .b, .c], then
\texttt{del} $x$[1] results in $x$ = \texttt{dict}\{ 0:.a, 2:.c \}, \emph{not}
$x$ = [.a, .c].
Harmony also does not support special slicing syntax like Python.
To modify lists, use the \texttt{subseq} method in the \texttt{list} module
(\autoref{ap:list}).

>>>>

Details:
\begin{itemize}
\item The name in a name tag is the name of the method that the process
is executing;
\item The tag in a name tag the argument to the method by default.  Optionally
\texttt{spawn} allows the tag to be specified explicitly;
\item The frame pointer points to the current \emph{stack frame},
which consists of the caller's frame pointer and variables, the argument to
the method, an ``invocation type atom'' (\texttt{normal}, \texttt{interrupt}, or
\texttt{process}), and the return address (in case of \texttt{normal}).
\item A process terminates when it reaches the \texttt{Return} instruction
of the top-level method (when the stack frame is of type \texttt{process})
or when it hits an exception.  Exceptions include divide by zero,
reading a non-existent key in a dictionary, accessing a non-existent
variable, infinite loops of microsteps, as well as when an assertion fails;
\item The execution of a process in \emph{atomic mode} does not get interleaved
with that of other processes.
\item The register of a process always contains a dictionary, mapping
atoms to arbitrary values.  The atoms correspond to the variable names
in a Harmony program.
\end{itemize}

@@

Consecutive macro steps by the same process are called \emph{mega steps}.
Each state maintains the shortest path to it from the initial state in terms
of mega steps.
The diameter of the graph is the length of the longest path found.

If some states have a problem, the state with the shortest path is reported.
Problematic states include states that experienced exceptions.
If there are no exceptions, Harmony computes the strongly connected components (SCCs)
of the graph (the number of such components are printed as part of the output).
The sink SCCs should each consist of a terminal state without any processes.
If not, again the state with the shortest path is reported.

If there are no problematic states, Harmony reports ``no issues found'' and outputs
in the HTML file the state with the longest path.

@@

Because tuples and lists are dictionaries, the \texttt{del} statement is
different than in Python.  For example, if $x$ = [.a, .b, .c], then
\texttt{del} $x$[1] results in $x$ = \texttt{dict}\{ 0:.a, 2:.c \}, \emph{not}
$x$ = [.a, .c].
Harmony also does not support special slicing syntax like Python.
To modify lists, use the \texttt{subseq} method in the \texttt{list} module
(\autoref{ap:list}).
